Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2017-12-18 pkg/disttree/inst/draft/draft.Rnw
comments TH
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1891 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 3ef54735073fbcd974b60f9b815351ab387000f6

\Abstract{
While many regression models consider only the mean of the response variable recent advances in parametric modeling have made it possible to model all distribution parameters. In that way the underlying distribution can be fully specified allowing for a wide range of analysis and prediction methods which are particularly valuable in applications such as probabilistic weather forecasting. In generalized additive models for location, scale and shape (GAMLSS, \citealt{stasinopoulos2005}) each distribution parameter can be modeled separately by its own generalized additive model (GAM) capturing linear and non-linear effects. A different approach that would make it possible to also model non-additive effects and interactions is to apply tree-structured models such as regression trees (\citealt{loh2011classification}) or random forests (\citealt{breiman2001random}). This class of models will now be integrated in probabilistic forecasting providing a novel general distributional framework for these methods. In particular, we are going to introduce distributional trees and forests which embed the idea of flexible parametric modeling into the framework of regression trees and random forests. Applying these novel approaches to precipitation data in a mountainous region with a very large number of numerical weather prediction quantities shows one of their main advantages in selecting variables automatically and illustrates their strengths as their performance is compared to GAMLSS models that are specified based either on subject-matter knowledge and experience from meteorology or based on a computationally more demanding boosting approach.

@@

  Torsten Hothorn\\
  Institut f\"ur Sozial- und Pr\"aventivmedizin, Abteilung Biostatistik \\
  Universit\"at Z\"urich \\
  Hirschengraben 84\\
  CH-8001 Z\"urich, Switzerland \\
  E-mail: \email{Torsten.Hothorn@R-project.org}\\
  URL: \url{http://user.math.uzh.ch/hothorn/}\\

@@

\SweaveOpts{eval = TRUE}
\section{Introduction}
In regression analysis various models have been developed to describe the relationship between a response variable and a (set of) covariate(s). Starting from linear models (LM) being extended to generalized linear models (GLM) the limitation to model only linear effects has lead to the development of generalized additive models (GAM) also capturing non-linear effects as illustrated in Figure~\ref{Devel_parmod}. These models consider only the expectation of the underlying distribution, however, in recent years there has been a paradigm shift from regression models for the mean to distributional regression approaches for probabilistic forecasting. For example in the field of precipitation forecasting linear models such as ensemble model output statistics (EMOS, \citealt{gneiting2005calibrated}) usually acting on the assumption of a normally distributed response variable allow for both parameters, the mean and the variance, to depend linearly on covariates. Based on the resulting model the probability of precipitation can be estimated as well as the expected amount of precipitation. Therefore, these models provide common and widely used tools, also due to their intuitive structure and interpretability. However, the restriction to model only linear effects has risen the interest in applying more flexible models. Generalized additive models for location, scale and shape (GAMLSS, \citealt{stasinopoulos2005}) offer a framework in which each distribution parameter can be modeled separately by its own GAM. These flexible parametric methods provide well fitting models when applied on precipitation data in a rather smooth and homogeneous setting, e.g. areas where no abrupt changes in meteorological/climatological events appear. However, for example in complex terrain in mountainous regions various factors can change rapidly and their effects are difficult to be represented by a smooth parametric model. In this situation a different approach which can deal with these abrupt changes would be to apply tree-structured models such as regression trees (\citealt{loh2011classification}) or random forests (\citealt{breiman2001random}). Moreover, these models are particularly advantageous in case of many covariates with unknown effects or interactions as the variable selection is done automatically within the model fitting process. Therefore, no additional effort or knowledge for the specification of the model is required in advance. However, even though their main advantage of being able to model non-additive effects and interactions without any necessary prespecification can play to their strength, regression trees are not an adequate choice if (additional) smooth effects appear as well. In this situation a random forest provides a good compromise as it combines a set of trees such that the steps imposed by the trees are smoothed out in case of smooth effects while abrupt changes are still captured by the tree structure of the model.

For these reasons, regression trees and particularly random forests provide valuable features which can contribute to improving models for probabilistic forecasting. Therefore, we are going to introduce a novel general distributional framework for these methods by presenting distributional trees and forests which embed the idea of flexible parametric modeling into the framework of regression trees and random forests. The developments in the field of tree-structured models together with the novel approaches of distributional trees and forests are illustrated in Figure~\ref{Devel_treeforest}.

@@

After explaining the novel methodology in Section~\ref{Methodology} of this paper the focus will then be put on an application in the field of probabilistic forecasting in Section~\ref{ProbabilisticForecasting}. The new method is applied on precipitation data in a mountainous region with a very large number of numerical weather prediction quantities and the results are compared to those of other methods commonly used in this research area. In a first setting only one observation station is taken into consideration. The models are trained on data from 24 years and probabilistic predictions of the consecutive 4 years are validated. A brief outlook on the results of this setting is given by Figure~\ref{axams_onestation}. For the 24th of July of 2009, 2010, 2011 and 2012 the density functions of the distributions estimated by a forest model are plotted together with the corresponding observations. This illustrates that well fitting predicted expected values are provided by this model as they are close to the observed values. Beside the expected values the predictions provided by distributional models offer a wide range of information as they specify the whole distribution and therefore enable further methods of inference and analysis. In section \ref{ProbabilisticForecasting} this example will be further discussed and it will be shown that the predictions made by the forest model are reasonably well fitting, not only for the mean parameter of the distribution but also for its second parameter, the scale parameter, and therefore the whole distribution.

@@

\subsection{Distributional fit}
\label{distfit}
Fitting a distributional model to a set of observations without considering any covariates is a well known procedure which can for example be done by applying the maximum likelihood method. This is also the chosen approach in the methodology described in this section.

@@

\subsection{Distributional tree}
\label{disttree}
Given the fit of a global distributional model $D(Y, \bold{\hat{\theta}})$ the idea is to use the information provided by this model together with a set of covariates $\bold{Z} = (Z_1, \ldots, Z_m) \in \mathcal{Z}$ (from now on denoted by $\bold{Z}$ instead of $\bold{X}$ to indicate that they are considered as split variables only and not as regressors) to decide whether the data set should be split into subgroups or not. In particular, the information provided by the fitted model are the scores 
$$
s(\hat{\theta}, y_i) = \frac{\partial \ell}{\partial \theta}(\hat{\theta}; y_i).
$$ 
These values express how well the model fits the data regarding each parameter. Ideally they should fluctuate randomly around zero, similar to residuals in ordinary least squares estimations, but in this case there is a score value for each pair of estimated parameter $\hat{\theta}_j \in (\hat{\theta}_1, \ldots, \hat{\theta}_k) = \bold{\hat{\theta}}$ and observation $y_j \in \{y_i\}_{i = 1,\ldots, n}$. This enables the model to be sensitive to changes in each of the parameters which is one of the main advantages of distributional trees over other tree models considering only the mean of the distribution.

@@

In a next step a local distributional model is fit in each of the subgroups. Repeating this procedure of fitting a model, applying statistical tests to evaluate the goodness of fit and splitting the data set depending on the test results leads to a tree structure. In that way the learning data set is separated into \textit{B} disjoint segments such that
$$
\mathcal{Z} = \dot{\bigcup\limits_{b = 1, \ldots, \textit{B}}} \mathcal{B}_b
$$
where each segment is represented by a terminal node of the tree.

The exact way of determining how and where to split varies across different tree algorithms. For distributional trees, one of two algorithms can be chosen as a framework to build the tree: either the MOB algorithm (\citealt{zeileis2008model}) or the ctree algorithm (\citealt{hothorn2006unbiased}). Summed up, the steps of building a distributional tree using one of these algorithms are
\begin{enumerate}
\item Specify a distribution with log-likelihood function $\ell(\theta; y)$.
\item Estimate $\bold{\hat{\theta}}$ via maximum likelihood.
\item Test for associations or instabilities of the scores $s(\bold{\hat{\theta}}, y_i)$ and each partitioning variable $Z_l$.
%\item Assess whether the \emph{model scores} are associated with
%    (or change along) any of the available covariates -- e.g.,
%    using parameter instability tests (\emph{strucchange}) or
%    conditional inference (\emph{coin}).
\item Split the sample along the partitioning variable with the strongest association or instability.
    Choose the breakpoint with the highest improvement in log-likelihood.
\item Repeat steps 2--4 recursively in the subgroups
    until some stopping criterion is reached.
    %-- e.g., for significance or sample size.
%\item Choose the variable with the strongest association
%\item Choose the split point which leads to the highest improvement of the model
%\item Split and repeat 2-6 in each node until a stopping criterion is met
\end{enumerate}
The stopping criterion in step 5 can for example be a minimum number of observations in a node or a p-value for the statistical tests applied in step 3.

@@

For distributional trees the strategy of how to make a prediction for a new set of covariates $\bold{z}^{\ast} = (z_1^{\ast}, \ldots, z_m^{\ast})$ is very simple and straight forward. All observations of the learning data set $\{(y_i,\bold{z}_i)\}_{i=1\ldots,n}$ which end up in the same terminal node of the tree as the new set of covariates are selected and a distributional model is fit on the subset. To select this subset a weight vector $\bold{\omega}^{tree} = (\omega^{tree}_1, \ldots, \omega^{tree}_n)$ is included in the fitting process.
$$
\omega^{tree}_i(\bold{z}^{\ast}) = \sum_{b=1}^B I((\bold{z}_i \in \mathcal{B}_b) \land (\bold{z}^{\ast} \in \mathcal{B}_b))
$$
The predicted distribution of the new set of covariates is then fully specified by the estimated parameter $\hat{\theta}(\bold{z}^{\ast})$ where
$$
\hat{\theta}(\bold{z}^{\ast}) = \max_{\theta \in \Theta} \sum_{i=1}^n \omega^{tree}_i(\bold{z}^{\ast}) \cdot \ell(\theta; y_i).
$$

@@

Common forest models such as random forests consist of trees only considering the mean of the distribution of the response variable. For that reason, changes in other parameters can only be detected if they are connected to changes in the location parameter, e.g. if they depend on the location parameter. Therefore, building a forest of distributional trees which can also capture separate effects in each of the distribution parameters leads to an improvement of the model. This valuable feature of detecting separate effects is also provided by GAMLSS as each parameter is modeled separately. However, in this case this separation can also be a disadvantage as it hinders the capturing of interactions unless they are specified explicitly by the user. These two cases provide once again a good reason to combine the two frameworks of flexible parametric modeling and tree-structured models in order to profit from their advantages and compensate possible disadvantages. This is the pursued goal in introducing distributional forests.

@@

Contrary to distributional trees, in distributional forests the whole learning data set can be used to fit the distributional model and specify the predicted distribution for a new set of covariates. This difference is represented in the weight vector as the tree weights $\bold{\omega}^{tree}$ containing only zeros and ones are now replaced by integer valued forest weights

@@

For a new set of covariates $\bold{z}^{\ast} = (z^{\ast}_1, \ldots, z^{\ast}_m) $ the set of weights is obtained by the following procedure: For each tuple $(y_j,\bold{z}_j)$ in the learning data set $\{(y_i,\bold{z}_i)\}_{i=1\ldots,n}$ a weight is calculated by counting the number of trees in which $(y_j,\bold{z}_j)$ ends up in the same terminal node as the new set of covariates $\bold{z}^{\ast}$. 
$$
\omega^{forest}_i(\bold{z}^{\ast}) = \sum_{s=1}^T \sum_{b=1}^{B^s} I((\bold{z}_i \in \mathcal{B}^s_b) \land (\bold{z}^{\ast} \in \mathcal{B}^s_b))
$$
where $T$ is the number of trees of the forest, $B^s$ is the number of terminal nodes of the \textit{s}-th tree and $\mathcal{B}^s_b$ represents the \textit{b}-th terminal node of the \textit{s}-th tree.\\
This individual set of weights $\bold{\omega}^{forest}(\bold{z}^{\ast}) = (\omega^{forest}_1(\bold{z}^{\ast}), \ldots, \omega^{forest}_n(\bold{z}^{\ast}))$ for the new set of covariates $\bold{z}^{\ast}$ can now be included in the estimation process of the distribution parameters and in that way leads to its individual parameter vector $\hat{\theta}(\bold{z}^{\ast})$.
$$
\hat{\theta}(\bold{z}^{\ast}) =  \max_{\theta \in \Theta} \sum_{i=1}^n \omega^{forest}_i(\bold{z}^{\ast}) \cdot \ell(\theta; y_i)
$$
While in a distributional tree the same distribution is specified for all sets of covariates being in the same node, a distributional forest predicts and fits a different distribution for each different set of covariates due to the individual weights calculated separately for each set of covariates.

@@

Even though many situations demand for the use of specifically tailored models providing the needed features and therefore being clearly advantageous and the best choice, it is often hard to tell in advance which features will be required. In these cases a distributional forest is a recommendable compromise providing reasonable models and performing well without any prespecification or additional knowledge needed in advance.

@@

To remove large parts of the skewness of precipitation data, a power transformation has been used frequently (Box and Cox 1964). In literature, cubic (\citealt{stidd1973}) or square root (\citealt{hutchinson1998b}) transformations have often been suggested but may vary for different climatic zones or temporal aggregation periods. In \citealt{stauffer2017a} optimization methods have been applied to find the best transformation factor which resulted in a value of $\frac{1}{1.6}$. Since the observation data set used for this optimization contains the observations considered in this article the same factor is chosen here for the power transformation of the response variable \emph{tp} (total precipitation). The resulting transformed variable is expected to be normally distributed and left censored at censoring point 0. For simplicity the same transformation has been chosen for the variable \emph{cape} (convective available potential energy).

@@

In order to compare the performance of the chosen methods, the continuous ranked probability score (CRPS) is calculated for each model. The CRPS measures the accuracy of a probabilistic model. For one observation $y$ with the predicted distribution function $F$ the CRPS value is calculated by
$$
\text{CRPS}(y, F) = \int_{-\infty}^\infty (F(z) - \mathbf{1}(y \leq z))^2 dz
$$
where \(\mathbf{1}\) is the indicator function.

@@

The results of fitting one distributional forest to the first 24 years of the data set and predicting the total amount of precipitation for one specific day of each of the four successive years have been shown in Figure~\ref{axams_onestation} as a motivational example for a probabilistic forecast. Staying with this fitted model we are now going to analyze variable importance of this forest model and compare its results to those of the GAM models and the EMOS model based on probability integral transform (PIT) histograms (\citealt{gneiting2007}).

As shown in Table~\ref{model_specification} the forest model includes all 82 covariates. A single tree model allows to easily analyze which covariates are used as split variables in the nodes and hence have an impact on the response variable. In a forest model though, for each of the trees a subset of these covariates is chosen randomly as possible split variables which is one of the reasons leading to different splitting variables being chosen in each tree. To get an overview of which covariates have the most influential effect on the response variable a standard measurement of variable importance for forest models has been applied. Based on the mean decrease in accuracy regarding the CRPS the 10 leading covariates of the above described forest model for station Axams learned on the first 24 year are listed in Figure~\ref{varimp}. As expected, the numerical forecast for total precipitation is the most influential variable. In particular, five variations of this variable are among the top ten of the list of covariates ordered by variable importance.

>>>>

\Abstract{
While many regression models consider only the mean of the response variable recent advances in parametric modeling have made it possible to model all distribution parameters. In that way the underlying distribution can be fully specified allowing for a wide range of analysis and prediction methods which are particularly valuable in applications such as probabilistic weather forecasting. In generalized additive models for location, scale and shape (GAMLSS, \citealt{stasinopoulos2005}) each distribution parameter can be modeled separately by its own generalized additive model (GAM) capturing linear and non-linear effects. A different approach that would make it possible to also model non-additive effects and interactions is to apply tree-structured models such as regression trees (\citealt{loh2011classification}) or random forests (\citealt{breiman2001random}). 
%%%<TH> no references in abstract </TH>
This class of models 
%%%<TH> "this" means trees and forests? </TH>
will now be integrated in probabilistic forecasting providing a novel general distributional framework for these methods. In particular, we are going to introduce distributional trees and forests which embed the idea of flexible parametric modeling into the framework of regression trees and random forests. 
%%%<TH> break-up very long sentence </TH>
Applying these novel approaches to precipitation data in a mountainous region with a very large number of numerical weather prediction quantities shows one of their main advantages in selecting variables automatically and illustrates their strengths as their performance is compared to GAMLSS models that are specified based either on subject-matter knowledge and experience from meteorology or based on a computationally more demanding boosting approach.

@@

  Torsten Hothorn\\
  Institut f\"ur Epidemiologie, Biostatistik und Pr\"avention \\
  Universit\"at Z\"urich \\
  Hirschengraben 84\\
  CH-8001 Z\"urich, Switzerland \\
  E-mail: \email{Torsten.Hothorn@R-project.org}\\
  URL: \url{http://user.math.uzh.ch/hothorn/}\\

@@

\SweaveOpts{eval = TRUE}
\section{Introduction}
In regression analysis various models have been developed to describe the relationship between a response variable and a (set of) covariate(s). Starting from linear models (LM) being extended to generalized linear models (GLM) the limitation to model only linear effects has lead to the development of generalized additive models (GAM) also capturing non-linear effects as illustrated in Figure~\ref{Devel_parmod}. 
%%%<TH> more explantion for Fig 1 needed </TH>
These models consider only the expectation of the underlying distribution, however, in recent years there has been a paradigm shift from regression models for the mean to distributional regression approaches for probabilistic forecasting. For example in the field of precipitation forecasting linear models such as ensemble model output statistics (EMOS, \citealt{gneiting2005calibrated}) usually acting on the assumption of a normally distributed response variable allow for both parameters, the mean and the variance, to depend linearly on covariates. Based on the resulting model the probability of precipitation can be estimated as well as the expected amount of precipitation. Therefore, these models provide common and widely used tools, also due to their intuitive structure and interpretability. However, the restriction to model only linear effects has risen the interest in applying more flexible models. Generalized additive models for location, scale and shape (GAMLSS, \citealt{stasinopoulos2005}) offer a framework in which each distribution parameter can be modeled separately by its own GAM. These flexible parametric methods provide well fitting models when applied on precipitation data in a rather smooth and homogeneous setting, e.g. areas where no abrupt changes in meteorological/climatological events appear. However, for example in complex terrain in mountainous regions various factors can change rapidly and their effects are difficult to be represented by a smooth parametric model. In this situation a different approach which can deal with these abrupt changes would be to apply tree-structured models such as regression trees 
%%%<TH> citation Loh does not fit, maybe omit citations anyway </TH>
(\citealt{loh2011classification}) or random forests (\citealt{breiman2001random}). Moreover, these models are particularly advantageous in case of many covariates with unknown effects or interactions as the variable selection is done automatically within the model fitting process. Therefore, no additional effort or knowledge for the specification of the model is required in advance. However, even though their main advantage of being able to model non-additive effects and interactions without any necessary prespecification can play to their strength, regression trees are not an adequate choice if (additional) smooth effects appear as well. In this situation a random forest provides a good compromise as it combines a set of trees such that the steps imposed by the trees are smoothed out in case of smooth effects while abrupt changes are still captured by the tree structure of the model.

For these reasons, regression trees and particularly random forests provide valuable features which can contribute to improving models for probabilistic forecasting. Therefore, we are going to introduce a novel general distributional framework for these methods by presenting distributional trees and forests which embed the idea of flexible parametric modeling into the framework of regression trees and random forests. The developments in the field of tree-structured models together with the novel approaches of distributional trees and forests are illustrated in Figure~\ref{Devel_treeforest}.
%%% <TH> better description for Fig 2 </TH>

@@

After explaining the novel methodology in Section~\ref{Methodology} of this paper the focus will then be put on an application in the field of probabilistic forecasting in Section~\ref{ProbabilisticForecasting}. The new method is applied on precipitation data in a mountainous region with a very large number of numerical weather prediction quantities and the results are compared to those of other methods commonly used in this research area. In a first setting only one observation station is taken into consideration. The models are trained on data from 24 years and probabilistic predictions of the consecutive 4 years are validated. A brief outlook on the results of this setting is given by Figure~\ref{axams_onestation}. For the 24th of July of 2009, 2010, 2011 and 2012 the density functions of the distributions estimated by a forest model are plotted together with the corresponding observations. This illustrates that well fitting predicted expected values 
%%% well fitting predicted expected values -> appropriate probabilistic forecasts? </TH>
are provided by this model as they are close to the observed values. Beside the expected values the predictions provided by distributional models offer a wide range of information as they specify the whole distribution and therefore enable further methods of inference and analysis. In section \ref{ProbabilisticForecasting} this example will be further discussed and it will be shown that the predictions made by the forest model are reasonably well fitting, not only for the mean parameter of the distribution but also for its second parameter, the scale parameter, and therefore the whole distribution.

@@

\subsection{Distributional fit}
\label{distfit}
Fitting a distributional model to a set of observations without considering any covariates is a well known procedure which can for example be done by applying the maximum likelihood method. This is also the chosen approach in the methodology described in this section. %%% <TH> is is repeated on page 5, remove here </TH>

@@

\subsection{Distributional tree}
\label{disttree}
Given the fit of a global distributional model $D(Y, \bold{\hat{\theta}})$ the idea is to use the information provided by this model together with a set of covariates $\bold{Z} = (Z_1, \ldots, Z_m) \in \mathcal{Z}$ (from now on denoted by $\bold{Z}$ instead of $\bold{X}$ to indicate that they are considered as split variables only and not as regressors)
%%% <TH> X -> Z is confusing. Either we always write theta = g(X) where
%%% g is now a tree or we explain that theta = g(X)(Z) is what we want.
%%% Here, we don't partition models with X variables, so we should stick to X. </TH>
to decide whether the data set should be split into subgroups or not. In particular, the information provided by the fitted model are the scores 
$$
s(\hat{\theta}, y_i) = \frac{\partial \ell}{\partial \theta}(\hat{\theta}; y_i).
$$ 
These values express how well the model fits the data regarding each parameter. Ideally they should fluctuate randomly around zero, similar to residuals in ordinary least squares estimations, but in this case there is a score value for each pair of estimated parameter $\hat{\theta}_j \in (\hat{\theta}_1, \ldots, \hat{\theta}_k) = \bold{\hat{\theta}}$ and observation $y_j \in \{y_i\}_{i = 1,\ldots, n}$. This enables the model to be sensitive to changes in each of the parameters which is one of the main advantages of distributional trees over other tree models considering only the mean of the distribution.

@@

In a next step a local distributional model is fit in each of the subgroups. Repeating this procedure of fitting a model, applying statistical tests to evaluate the goodness of fit %%%<TH> avoid goodness of fit, this term is too ambiguous here </TH>
and splitting the data set depending on the test results leads to a tree structure. In that way the learning data set is separated into \textit{B} disjoint segments such that
$$
\mathcal{Z} = \dot{\bigcup\limits_{b = 1, \ldots, \textit{B}}} \mathcal{B}_b
$$
where each segment is represented by a terminal node of the tree.

The exact way of determining how and where to split varies across different tree algorithms. For distributional trees, one of two algorithms can be chosen as a framework to build the tree: either the MOB algorithm (\citealt{zeileis2008model}) or the ctree algorithm (\citealt{hothorn2006unbiased}). Summed up, the steps of building a distributional tree using one of these algorithms are
\begin{enumerate}
\item Specify a distribution with log-likelihood function $\ell(\theta; y)$.
\item Estimate $\bold{\hat{\theta}}$ via maximum likelihood.
\item Test for associations or instabilities of the scores $s(\bold{\hat{\theta}}, y_i)$ and each partitioning variable $Z_l$.
%\item Assess whether the \emph{model scores} are associated with
%    (or change along) any of the available covariates -- e.g.,
%    using parameter instability tests (\emph{strucchange}) or
%    conditional inference (\emph{coin}).
\item Split the sample along the partitioning variable with the strongest association or instability.
    Choose the breakpoint with the highest improvement in log-likelihood.
\item Repeat steps 2--4 recursively in the subgroups
    until some stopping criterion is reached.
    %-- e.g., for significance or sample size.
%\item Choose the variable with the strongest association
%\item Choose the split point which leads to the highest improvement of the model
%\item Split and repeat 2-6 in each node until a stopping criterion is met
\end{enumerate}
The stopping criterion in step 5 can for example be a minimum number of observations in a node or a p-value for the statistical tests applied in step 3.
%%% <TH> we need a little more detail here or a reference to a better
%%% description of mob/ctree </TH>

@@

For distributional trees the strategy of how to make a prediction for a new set of covariates $\bold{z}^{\ast} = (z_1^{\ast}, \ldots, z_m^{\ast})$ 
%%% <TH> \bold{z} is sufficient, remove ^\ast </TH>
is very simple and straight forward. 
%%% <TH> better avoid this judgement </TH>
All observations of the learning data set $\{(y_i,\bold{z}_i)\}_{i=1\ldots,n}$ which end up in the same terminal node of the tree as the new set of covariates are selected and a distributional model is fit on the subset. To select this subset a weight vector $\bold{\omega}^{tree} = (\omega^{tree}_1, \ldots, \omega^{tree}_n)$ is included in the fitting process.
%%% <TH> tree -> \text{tree}
$$
\omega^{tree}_i(\bold{z}^{\ast}) = \sum_{b=1}^B I((\bold{z}_i \in \mathcal{B}_b) \land (\bold{z}^{\ast} \in \mathcal{B}_b))
$$
The predicted distribution of the new set of covariates is then fully specified by the estimated parameter $\hat{\theta}(\bold{z}^{\ast})$ where
$$
\hat{\theta}(\bold{z}^{\ast}) = \max_{\theta \in \Theta} \sum_{i=1}^n \omega^{tree}_i(\bold{z}^{\ast}) \cdot \ell(\theta; y_i).
$$

@@

%%% <TH> we need to be much more precise here: random forests is Breiman's and Cutler's
%%% random forest. Maybe it is better to not mention this method at any time. </TH>
Common forest models such as random forests consist of trees only considering the mean of the distribution of the response variable. For that reason, changes in other parameters can only be detected if they are connected to changes in the location parameter, e.g. if they depend on the location parameter. Therefore, building a forest of distributional trees which can also capture separate effects in each of the distribution parameters leads to an improvement of the model. This valuable feature of detecting separate effects is also provided by GAMLSS as each parameter is modeled separately. However, in this case this separation can also be a disadvantage as it hinders the capturing of interactions unless they are specified explicitly by the user. These two cases provide once again a good reason to combine the two frameworks of flexible parametric modeling and tree-structured models in order to profit from their advantages and compensate possible disadvantages. This is the pursued goal in introducing distributional forests.

@@

Contrary to distributional trees, in distributional forests the whole learning data set can be used to fit the distributional model and specify the predicted distribution for a new set of covariates. This difference is represented in the weight vector as the tree weights $\bold{\omega}^{tree}$ containing only zeros and ones are now replaced by integer valued forest weights 
%%% <TH> we need references for the nearest neighbor weights, copy from
%%% "Transformation Forests" </TH>
%%% <TH> tree -> \text{tree}, forest -> \text{forest} </TH>

@@

For a new set of covariates $\bold{z}^{\ast} = (z^{\ast}_1, \ldots, z^{\ast}_m) $ the set of weights is obtained by the following procedure: For each tuple $(y_j,\bold{z}_j)$ in the learning data set $\{(y_i,\bold{z}_i)\}_{i=1\ldots,n}$ a weight is calculated by counting the number of trees in which $(y_j,\bold{z}_j)$ ends up in the same terminal node as the new set of covariates $\bold{z}^{\ast}$:
$$
\omega^{forest}_i(\bold{z}^{\ast}) = \sum_{s=1}^T \sum_{b=1}^{B^s} I((\bold{z}_i \in \mathcal{B}^s_b) \land (\bold{z}^{\ast} \in \mathcal{B}^s_b))
$$
where $T$ is the number of trees of the forest, $B^s$ is the number of terminal nodes of the \textit{s}-th tree and $\mathcal{B}^s_b$ represents the \textit{b}-th terminal node of the \textit{s}-th tree.\\

%%%<TH> we need to cite "Transformation Forests" for the interpretation of
%%% random forests as adaptive nearest neighbors </TH>

This individual set of weights $\bold{\omega}^{forest}(\bold{z}^{\ast}) = (\omega^{forest}_1(\bold{z}^{\ast}), \ldots, \omega^{forest}_n(\bold{z}^{\ast}))$ for the new set of covariates $\bold{z}^{\ast}$ can now be included in the estimation process of the distribution parameters and in that way leads to its individual parameter vector $\hat{\theta}(\bold{z}^{\ast})$.
$$
\hat{\theta}(\bold{z}^{\ast}) =  \max_{\theta \in \Theta} \sum_{i=1}^n \omega^{forest}_i(\bold{z}^{\ast}) \cdot \ell(\theta; y_i)
$$
While in a distributional tree the same distribution is specified for all sets of covariates being in the same node, a distributional forest predicts and fits a different distribution for each different set of covariates due to the individual weights calculated separately for each set of covariates.

@@

%%% <TH> this should go into the discussion or the interpretation of the
%%% empirical results </TH>
Even though many situations demand for the use of specifically tailored models providing the needed features and therefore being clearly advantageous and the best choice, it is often hard to tell in advance which features will be required. In these cases a distributional forest is a recommendable compromise providing reasonable models and performing well without any prespecification or additional knowledge needed in advance.

@@

%%% <TH> hm, now we _are_ using a transformation model without estimating the
%%% transformation. </TH>
To remove large parts of the skewness of precipitation data, a power transformation has been used frequently (Box and Cox 1964). In literature, cubic (\citealt{stidd1973}) or square root (\citealt{hutchinson1998b}) transformations have often been suggested but may vary for different climatic zones or temporal aggregation periods. In \citealt{stauffer2017a} optimization methods have been applied to find the best transformation factor which resulted in a value of $\frac{1}{1.6}$. Since the observation data set used for this optimization contains the observations considered in this article the same factor is chosen here for the power transformation of the response variable \emph{tp} (total precipitation). The resulting transformed variable is expected to be normally distributed and left censored at censoring point 0. For simplicity the same transformation has been chosen for the variable \emph{cape} (convective available potential energy).

@@

In order to compare the performance of the chosen methods, the continuous ranked probability score (CRPS) is calculated for each model. The CRPS measures the accuracy of a probabilistic model. For one observation $y$ with the predicted distribution function $F$ the CRPS value is calculated by
$$
\text{CRPS}(y, F) = \int_{-\infty}^\infty (F(z) - \mathbf{1}(y \leq z))^2 dz
$$
where \(\mathbf{1}\) is the indicator function.
%%% <TH> y > z??? </TH>

@@

The results of fitting one distributional forest to the first 24 years of the data set and predicting the total amount of precipitation for one specific day of each of the four successive years have been shown in Figure~\ref{axams_onestation} as a motivational example for a probabilistic forecast. Staying with this fitted model we are now going to analyze variable importance of this forest model and compare its results to those of the GAM models and the EMOS model based on probability integral transform (PIT) histograms (\citealt{gneiting2007}).
%%% <TH> wouldn't be a uniform QQ-plot be more appropriate? </TH>

%%%<TH> always us the term "distributional forest"
As shown in Table~\ref{model_specification} the forest model includes all 82 covariates. A single tree model allows to easily analyze which covariates are used as split variables in the nodes and hence have an impact on the response variable. In a forest model though, for each of the trees a subset of these covariates is chosen randomly as possible split variables which is one of the reasons leading to different splitting variables being chosen in each tree. To get an overview of which covariates have the most influential effect on the response variable a standard measurement of variable importance for forest models has been applied. Based on the mean decrease in accuracy regarding the CRPS the 10 leading covariates of the above described forest model for station Axams learned on the first 24 year are listed in Figure~\ref{varimp}. As expected, the numerical forecast for total precipitation is the most influential variable. In particular, five variations of this variable are among the top ten of the list of covariates ordered by variable importance.
